Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-09-26 manuscripts/reply/reply-main.tex
Incorporating edits from proofs.

However, \citet{Hickerson2013} conclude that the bias is caused by numerical-
approximation error due to insufficient computation
(Hypothesis~\ref{hypError}).
They argue the widest of the three priors on divergence times used by
\citet{Oaks2012} would infrequently produce random samples of parameter values
with many independent population divergence times as recent as the estimated
gene divergence times presented in \citet{Oaks2012}.
% They also also suggest that Oaks et al.'s \citeyear{Oaks2012} estimated gene
% divergence times should be used to set the upper bound of the uniform prior on
% divergence times for the \msb analysis of the same sequence data.
% Given the gene-tree estimates were intended to provide only a rough comparison
% of the gene divergence times across the 22 taxa \citep{Oaks2012}, and our
% findings presented above regarding the behavior of \msb when empirically
% informed uniform priors are employed, such an approach should not be used.
However, this sampling-probability argument is based on some questionable
assumptions.
Oaks et al.'s (\citeyear{Oaks2012}) gene-tree estimates were intended to
provide only a rough comparison of the gene divergence times across the 22 taxa
and assumed an arbitrary strict per-site rate of $2\e{-8}$ mutations per
generation for all taxa.
Furthermore, because the branch-length units of the gene trees are in millions
of years whereas the divergence-time prior of \msb is in generations,
\citet{Hickerson2013} make the implicit assumption that all 22 Philippine taxa
have a generation time of one year.
More importantly, even if we assume (1) the arbitrary strict clock is correct,
(2) gene divergence times were estimated without error, and (3) all 22 taxa
have one-year generation times, Hickerson et al.'s (\citeyear{Hickerson2013})
argument actually demonstrates that the models used by \citet{Oaks2012} with
narrower priors on divergence times are densely populated with samples with
large numbers of divergence parameters with values younger than the estimated
gene divergence estimates.
Thus, if \citet{Hickerson2013} are correct, analyses under these narrow priors
should be much less biased toward clustered models of divergence.
However, the magnitude of the bias is very similar across all three priors
explored by \citet{Oaks2012}.
\citet{Hickerson2013} point out a case where the narrowest prior performs
slightly better (panel L of Figures S32, S37, and S38 of \citet{Oaks2012}).
However, it is important to note that these results suffered from a bug in
\msb, and after \citet{Oaks2012} corrected the bug, there are many cases where
the narrowest prior performs slightly worse (see panels D--J of Figures 3 and
S12).

>>>>

However, \citet{Hickerson2013} conclude that the bias is caused by numerical-
approximation error due to insufficient computation
(Hypothesis~\ref{hypError}).
They argue the widest of the three priors on divergence times used by
\citet{Oaks2012} would infrequently produce random samples of parameter values
with many independent population divergence times as recent as the estimated
gene divergence times presented in \citet{Oaks2012}.
% They also also suggest that Oaks et al.'s \citeyear{Oaks2012} estimated gene
% divergence times should be used to set the upper bound of the uniform prior on
% divergence times for the \msb analysis of the same sequence data.
% Given the gene-tree estimates were intended to provide only a rough comparison
% of the gene divergence times across the 22 taxa \citep{Oaks2012}, and our
% findings presented above regarding the behavior of \msb when empirically
% informed uniform priors are employed, such an approach should not be used.
However, this sampling-probability argument is based on some questionable
assumptions.
Oaks et al.'s (\citeyear{Oaks2012}) gene-tree estimates were intended to
provide only a rough comparison of the gene divergence times across the 22 taxa
and assumed an arbitrary strict per-site rate of $2\e{-8}$ mutations per
generation for all taxa.
Furthermore, because the branch-length units of the gene trees are in millions
of years whereas the divergence-time prior of \msb is in generations,
\citet{Hickerson2013} make the implicit assumption that all 22 Philippine taxa
have a generation time of one year.
More importantly, even if we assume (1) the arbitrary strict clock is correct,
(2) gene divergence times were estimated without error, and (3) all 22 taxa
have one-year generation times, Hickerson et al.'s (\citeyear{Hickerson2013})
argument actually demonstrates that the models used by \citet{Oaks2012} with
narrower priors on divergence times are densely populated with samples with
large numbers of divergence parameters with values younger than the estimated
gene divergence estimates.
Thus, if \citet{Hickerson2013} are correct, analyses under these narrow priors
should be much less biased toward clustered models of divergence.
However, the magnitude of the bias is very similar across all three priors
explored by \citet{Oaks2012}.
\citet{Hickerson2013} point out a case where the narrowest prior performs
slightly better (panel L of Figures S32, S37, and S38 of \citet{Oaks2012}).
However, it is important to note that these results suffered from a bug in
\msb, and after \citet{Oaks2012} corrected the bug, there are many cases where
the narrowest prior performs slightly worse (see panels D--J of Figures 3 and
S12 of \citet{Oaks2012}).
